---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory.data <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of cleanventory.data is to provide easy access to the data sets as 
created by the [cleanventory](https://github.com/RaoulWolf/cleanventory) 
package. 

As such, it comes with no additional dependencies.



## Installation

You can install the development version of cleanventory.data like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(cleanventory.data)
str(tsca)
```

## Acknowledgement

This R package was developed by the EnviData initiative at the 
[Norwegian Geotechnical Institute (NGI)](https://www.ngi.no/eng) as part of the 
project 
[ZeroPM: Zero pollution of Persistent, Mobile substances](https://zeropm.eu/). 
This project has received funding from the European Union's Horizon 2020 
research and innovation programme under grant agreement No 101036756.

If you find this package useful and can afford it, please consider making a 
donation to a humanitarian non-profit organization, such as 
[Sea-Watch](https://sea-watch.org/en/). Thank you. 
