---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory.data <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cleanventory.data/workflows/R-CMD-check/badge.svg)](https://github.com/RaoulWolf/cleanventory.data/actions)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cleanventory.data/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cleanventory.data?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of cleanventory.data is to provide easy access to the data sets as 
created by the [cleanventory](https://github.com/RaoulWolf/cleanventory) 
package. 


cleanventory.data aims to have correctly identified all missing values in the 
data sets, all CAS Registry Numbers validated (when present) and additionally 
all special characters are transformed into ASCII characters. 

As such, it comes with no additional dependencies.

We suggest the following packages/functionalities in addition: 
[`bit64::as.integer64()`](https://cran.r-project.org/web/packages/bit64) to 
correctly handle the `us_tsca$cas_reg_no` column (kept as `double` for 
compatibility).

As of `r Sys.Date()`, the following inventories are included: 

| Chemical Inventory | Name   | Version(s)            | URL                                                                               |
|:------------------ |:------ |:--------------------- |:--------------------------------------------------------------------------------- |
| US EPA TSCA        | `us_tsca` | 2021-08               | https://www.epa.gov/tsca-inventory                                                |
| EU CLP Annex VI    | `eu_clp_09`</br>`eu_clp_10`</br>`eu_clp_13`</br>`eu_clp_14`</br>`eu_clp_15`</br>`eu_clp_17` | 9, 10, 13, 14, 15, 17 | https://echa.europa.eu/en/information-on-chemicals/annex-vi-to-clp                |
| EU ECI             | `eu_eci`   | *Unknown*             | https://echa.europa.eu/information-on-chemicals/ec-inventory                      |
| Japan NITE         | `jp_nite` | March 2022            | https://www.nite.go.jp/chem/english/ghs/ghs_download.html                         |
| New Zealand IoC    | `nz_ioc`  | December 2021         | https://www.epa.govt.nz/database-search/new-zealand-inventory-of-chemicals-nzioc/ |
| South Korea NCIS   | `kr_ncis` | 4 May 2022            | https://ncis.nier.go.kr/en/mttrList.do                                            |
| Australia HSIC     | `au_hcis` | *Unknown*             | http://hcis.safeworkaustralia.gov.au/HazardousChemical                            |
| Australia ICI      | `au_ici`  | 10 February 2022      | https://www.industrialchemicals.gov.au/search-inventory                           |
| Taiwan TCSI        | `tw_csi` | 1 January 2019, 8 September 2019 | https://gazette.nat.gov.tw/egFront/detail.do?metaid=73440&log=detailLog, https://gazette.nat.gov.tw/egFront/detail.do?metaid=78617&log=detailLog |
| Philippine ICCS    | `ph_iccs`</br>`ph_emb_mc_07`</br>`ph_emb_mc_08`  | 2017, 2020, 2021      | https://chemical.emb.gov.ph/?page_id=138 |
| Japan CSCL         | `jp_cscl_ecs`</br>`jp_cscl_nacs_1`</br>`jp_cscl_nacs_2` | 31 May 2022</br>31 May 2022</br>1 April 2022 | https://www.nite.go.jp/en/chem/chrip/chrip_search/sltLst|
| Canada DSL         | `ca_dsl`   | 14 June 2022          | https://pollution-waste.canada.ca/substances-search/Substance?lang=en |
| China IECSC        | `cn_iecsc` | 2013                  | https://www.mee.gov.cn/gkml/hbb/bgg/201301/t20130131_245810.htm |


## Installation

You can install the development version of cleanventory.data from 
[GitHub](https://github.com/) with:

```{r install}
#| eval = FALSE

# install.packages("remotes")
remotes::install_github("ZeroPM-H2020/cleanventory.data")
```


## Example

The data sets are immediately available when loading the package. 

```{r example}
library(cleanventory.data)
str(eu_clp_17)
```

## Acknowledgement

This R package was developed at the 
[Norwegian Geotechnical Institute (NGI)](https://www.ngi.no/eng) as part of the 
project 
[ZeroPM: Zero pollution of Persistent, Mobile substances](https://zeropm.eu/). 
This project has received funding from the European Union's Horizon 2020 
research and innovation programme under grant agreement No 101036756.

---

If you find this package useful and can afford it, please consider making a 
donation to a humanitarian non-profit organization, such as 
[Sea-Watch](https://sea-watch.org/en/). Thank you. 
