---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory.data <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cleanventory.data/workflows/R-CMD-check/badge.svg)](https://github.com/RaoulWolf/cleanventory.data/actions)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cleanventory.data/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cleanventory.data?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of cleanventory.data is to provide easy access to the data sets as 
created by the [cleanventory](https://github.com/RaoulWolf/cleanventory) 
package. 

As such, it comes with no additional dependencies.

We suggest the following packages/functionalities in addition: 
[`bit64::as.integer64()`](https://cran.r-project.org/web/packages/bit64) to 
correctly handle the `tsca$cas_reg_no` column (kept as `double` for 
compatibility).

As of `r Sys.Date()`, the following inventories are included: 

| Chemical Inventory | Name   | Version(s)            | URL                                                                               |
|:------------------ |:------ |:--------------------- |:--------------------------------------------------------------------------------- |
| US EPA TSCA        | `tsca` | 2021-08               | https://www.epa.gov/tsca-inventory                                                |
| ECHA CLP Annex VI  | `clp`  | 9, 10, 13, 14, 15, 17 | https://echa.europa.eu/en/information-on-chemicals/annex-vi-to-clp                |
| ECHA EC            | `ec`   | *Unknown*             | https://echa.europa.eu/information-on-chemicals/ec-inventory                      |
| Japan NITE         | `nite` | March 2022            | https://www.nite.go.jp/chem/english/ghs/ghs_download.html                         |
| New Zealand IoC    | `ioc`  | December 2021         | https://www.epa.govt.nz/database-search/new-zealand-inventory-of-chemicals-nzioc/ |
| South Korea NCIS   | `ncis` | 4 May 2022            | https://ncis.nier.go.kr/en/mttrList.do                                            |
| Australia HSIC     | `hcis` | *Unknown*             | http://hcis.safeworkaustralia.gov.au/HazardousChemical                            |
| Australia ICI      | `ici`  | 10 February 2022      | https://www.industrialchemicals.gov.au/search-inventory                           |


## Installation

You can install the development version of cleanventory.data from 
[GitHub](https://github.com/) with:

```{r install}
#| eval = FALSE

# install.packages("devtools")
remotes::install_github("ZeroPM-H202/cleanventory.data")
```


## Example

The data sets are immediately available when loading the package. 

```{r example}
library(cleanventory.data)
str(clp)
```

## Acknowledgement

This R package was developed by the EnviData initiative at the 
[Norwegian Geotechnical Institute (NGI)](https://www.ngi.no/eng) as part of the 
project 
[ZeroPM: Zero pollution of Persistent, Mobile substances](https://zeropm.eu/). 
This project has received funding from the European Union's Horizon 2020 
research and innovation programme under grant agreement No 101036756.

---

If you find this package useful and can afford it, please consider making a 
donation to a humanitarian non-profit organization, such as 
[Sea-Watch](https://sea-watch.org/en/). Thank you. 
