---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory.data <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cleanventory.data/workflows/R-CMD-check/badge.svg)](https://github.com/RaoulWolf/cleanventory.data/actions)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cleanventory.data/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cleanventory.data?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of cleanventory.data is to provide easy access to the data sets as 
created by the [cleanventory](https://github.com/RaoulWolf/cleanventory) 
package. 

As such, it comes with no additional dependencies.

We suggest the following packages/functionalities in addition: 
[`bit64::as.integer64()`](https://cran.r-project.org/web/packages/bit64) to 
correctly handle the `tsca$cas_reg_no` column (kept as `double` for 
compatibility), and 
[`textclean::replace_non_ascii()`](https://cran.r-project.org/web/packages/textclean) 
to replace non-ASCII characters with ASCII-equivalents for the `ec$ec_name` , 
`ec$description` and `ec$echa_name` columns (kept as is for transparency).

As of `r Sys.Date()`, the following inventories are included: 

| Chemical Inventory | Name   | Version(s)            | URL                                                                |
|:------------------ |:------ |:--------------------- |:------------------------------------------------------------------ |
| US EPA TSCA        | `tsca` | 2021-08               | https://www.epa.gov/tsca-inventory                                 |
| ECHA CLP Annex VI  | `clp`  | 9, 10, 13, 14, 15, 17 | https://echa.europa.eu/en/information-on-chemicals/annex-vi-to-clp |
| ECHA EC            | `ec`   | *Unknown*             | https://echa.europa.eu/information-on-chemicals/ec-inventory       |


## Installation

You can install the development version of cleanventory.data from 
[GitHub](https://github.com/) with:

```{r install}
#| eval = FALSE

# install.packages("devtools")
remotes::install_github("RaoulWolf/cleanventory.data")
```


## Example

The data sets are immediately available when loading the package. 

```{r example}
library(cleanventory.data)
str(clp)
```

## Acknowledgement

This R package was developed by the EnviData initiative at the 
[Norwegian Geotechnical Institute (NGI)](https://www.ngi.no/eng) as part of the 
project 
[ZeroPM: Zero pollution of Persistent, Mobile substances](https://zeropm.eu/). 
This project has received funding from the European Union's Horizon 2020 
research and innovation programme under grant agreement No 101036756.

If you find this package useful and can afford it, please consider making a 
donation to a humanitarian non-profit organization, such as 
[Sea-Watch](https://sea-watch.org/en/). Thank you. 
